Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-01-27 paper/paper.tex
Minor fixes

For typed graphs, morphisms between the graphs are typically defined between graphs typed over the
same type graph, but there are situations where we are interested in mapping between graphs typed
over different type graphs.  One such scenario from a software engineering context is described by
Dur{\'a}n et al.~\cite{Duran+12,Duran+17}, where graph transformation systems are composed by
defining morphisms between the rules constituting the respective transformation systems.  In this
case, the source and target transformation systems will normally have different type graphs, a
morphism must also be established between the two type graphs.  Mappings between the various graphs
making up the rules then need to preserve structure and typing subject to the morphism between type
graphs. This approach to specification composition is implemented by the gts-morpher
tool.\footnote{\url{https://github.com/gts-morpher/gts_morpher}} A key objective is to minimise the
amount of specification that needs to be written.  For example, the tool allows morphisms between
graph transformation systems to be only partially specified and then automatically completes the
full morphism, if it can do so unambiguously---this requires solving a sub-isomorphism problem.

>>>>

For typed graphs, morphisms between the graphs are typically defined between graphs typed over the
same type graph, but there are situations where we are interested in mapping between graphs typed
over different type graphs.  One such scenario from a software engineering context is described by
Dur{\'a}n et al.~\cite{Duran+12,Duran+17}, where graph transformation systems are composed by
defining morphisms between the rules constituting the respective transformation systems.  In this
case, the source and target transformation systems will normally have different type graphs; a
morphism must also be established between the two type graphs.  Mappings between the various graphs
making up the rules then need to preserve structure and typing subject to the morphism between type
graphs. This approach to specification composition is implemented by the GTSMorpher
tool.\footnote{\url{https://github.com/gts-morpher/gts_morpher}} A key objective is to minimise the
amount of specification that needs to be written.  For example, the tool allows morphisms between
graph transformation systems to be only partially specified and then automatically completes the
full morphism, if it can do so unambiguously---this requires solving a sub-isomorphism problem.
